\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{tcolorbox}
\tcbuselibrary{skins}

\definecolor{isaziteal}{HTML}{2AB6C4}
\definecolor{isazipink}{HTML}{C7327A}
\definecolor{isaziorange}{HTML}{F0803C}
\definecolor{isazigold}{HTML}{F0B429}

\titleformat{\section}{\Large\bfseries\color{isazipink}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\normalsize\bfseries\color{isaziteal}}{}{0em}{}

\newtcolorbox{scriptbox}{colback=gray!5,colframe=gray!40,fonttitle=\bfseries,title=SAY THIS (word-for-word),boxrule=0.6pt,arc=2pt}
\newtcolorbox{actionbox}{colback=isaziteal!8,colframe=isaziteal,fonttitle=\bfseries,title=DO THIS,boxrule=0.8pt,arc=2pt}
\newtcolorbox{notebox}{colback=isazigold!10,colframe=isaziorange,fonttitle=\bfseries,title=NOTE,boxrule=0.8pt,arc=2pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\small\color{gray}AI Middleman -- 30-Second Pitch (v2 -- July 2026)}
\fancyfoot[R]{\small\color{gray}\thepage}
\renewcommand{\headrulewidth}{0pt}

\title{\color{isazipink}\Huge AI Middleman\\\Large The 30-Second Pitch}
\author{}
\date{}

\begin{document}
\maketitle

\begin{tcolorbox}[colback=isazipink!6,colframe=isazipink,title=HOW TO USE THIS DOCUMENT,fonttitle=\bfseries]
This is the updated elevator pitch, revised to reflect the two major capabilities added in July 2026: the \textbf{update-approval gate} (Sam mentions a fact about a contact; Alex approves or ignores it before the database changes) and the \textbf{named-contact lookup} (``Do you know Kara Davis? Can I get her details?''). The core three-beat structure is unchanged: \textbf{Problem} $\to$ \textbf{Demo the solution} $\to$ \textbf{Close on the problem, in numbers}. Beat 2 now carries both the search-and-draft story and the self-updating network story --- they land as a single, richer capability rather than two features bolted together. Total spoken length is \textbf{81 words} ($\sim$32 seconds at a natural 150 wpm; $\sim$29 seconds at a brisker 170 wpm). \textbf{Rehearse out loud with a timer.}
\end{tcolorbox}

\section{The structure, at a glance}

\begin{center}
\begin{tabular}{@{}p{2.2cm}p{2cm}p{1.8cm}p{7.5cm}@{}}
\toprule
Beat & Time & Words & Job \\
\midrule
1. Problem & $\sim$11s & 27 & Make them feel it in one concrete moment, not an abstract claim \\
2. Demo the solution & $\sim$14s & 36 & Show \emph{both} capabilities: contact search + self-updating network \\
3. Close on the problem & $\sim$7s & 18 & Restate the problem, now solved --- in a number, naming who benefits \\
\bottomrule
\end{tabular}
\end{center}

\section{Beat 1 --- The Problem}

\begin{scriptbox}
``A friend texts you: `know a good lawyer in London?' The person's in your network somewhere --- but finding them, and writing the intro, eats your evening.''
\end{scriptbox}

\begin{notebox}
Unchanged from v1 --- it still works because it's a scene, not a statistic. The listener pictures their own phone. Don't generalise it. This beat hasn't changed because the problem hasn't changed.
\end{notebox}

\section{Beat 2 --- Demo the Solution}

\begin{scriptbox}
``Watch. Message comes in --- fifty thousand contacts searched, a draft in Alex's own voice, one tap to send. And when Sam mentions someone moved companies, Alex gets a single confirm button --- the network stays current by itself.''
\end{scriptbox}

\begin{actionbox}
If you have the app open, send the Beat-1 message as Sam right as you say ``Watch'' --- the 11-stage live pipeline stepper lights up in real time (received $\to$ checking $\to$ AI intent $\to$ matching $\to$ drafting $\to$ waiting on Alex) and does the visual work while you talk over it. For the second half of this beat (the network-update angle), send the update message: \textit{``Kara Davis left Andreessen Horowitz, she's at Bain Capital now''} --- Alex's phone shows a two-button \textbf{Update / Ignore} prompt; one tap and the database changes live on screen. That's the moment: the network maintains itself in the same conversation, no data-entry step, Alex stays in control.
\end{actionbox}

\begin{notebox}
Four things this beat does deliberately: (1) ``fifty thousand contacts'' gives scale a number; (2) ``in Alex's own voice'' signals this isn't a generic auto-reply --- the LLM drafts differently each time; (3) ``one tap to send'' keeps the human-in-the-loop point without spending a sentence on why it matters; (4) ``the network stays current by itself'' is the new hook --- it reframes the product from a search tool to a self-maintaining relationship graph that Alex controls. Do not say ``the AI updates the database'' --- that sounds autonomous and raises trust concerns. \emph{Alex} approves the update; say so if asked.
\end{notebox}

\section{Beat 3 --- Close on the Problem (with the number)}

\begin{scriptbox}
``That's an evening of digging turned into a ten-second tap --- for every well-connected professional who's tired of being their own CRM.''
\end{scriptbox}

\begin{notebox}
Updated from v1's close (``giving every well-connected professional their time back'') to add ``tired of being their own CRM'' --- this phrase lands harder now that the self-updating network is part of Beat 2. It names the exact frustration that makes the update-gate feature click: the connector already spends time maintaining contacts manually; this takes it off their plate. Don't rush this line --- slow down on ``tired of being their own CRM'' so it sticks.
\end{notebox}

\section{The full script, back to back}

\begin{tcolorbox}[colback=gray!5,colframe=isazipink,title={\textbf{Read this straight through, no pauses between beats}},fonttitle=\bfseries,boxrule=1pt,arc=3pt]
\itshape
``A friend texts you: `know a good lawyer in London?' The person's in your network somewhere --- but finding them, and writing the intro, eats your evening.

Watch. Message comes in --- fifty thousand contacts searched, a draft in Alex's own voice, one tap to send. And when Sam mentions someone moved companies, Alex gets a single confirm button --- the network stays current by itself.

That's an evening of digging turned into a ten-second tap --- for every well-connected professional who's tired of being their own CRM.''
\end{tcolorbox}

\section{If you're running long --- the 15-second cut}

For a genuinely tight window, drop straight to problem $\to$ close, skip the demo narration:

\begin{scriptbox}
``Networking pros lose an evening every time a friend asks for an intro --- and another hour keeping contacts up to date. AI Middleman turns both into a ten-second tap on WhatsApp.''
\end{scriptbox}

Use only as a true fallback --- it loses the demo beat entirely, and the demo is what makes people lean in. The update angle in this cut (``keeping contacts up to date'') earns its one extra phrase because it signals the product is broader than a search widget.

\section{What NOT to do in 30 seconds}
\begin{itemize}
    \item Don't mention the tech stack, Groq, Featherless, or the two-stage retrieval architecture --- save those for follow-up questions.
    \item Don't say ``the AI updates the database'' --- say ``Alex approves the update'' or ``one confirm button.'' The human-in-the-loop framing is a feature, not an asterisk; lead with it.
    \item Don't explain the 11-stage pipeline by name --- the live stepper on screen does that visually; your words should narrate the \emph{outcome}, not the mechanism.
    \item Don't hedge (``it's still a prototype, but\ldots'') inside the pitch. Confidence here, honesty later if asked.
    \item Don't rush the close. ``Tired of being their own CRM'' is the line that gets remembered --- slow down slightly rather than speeding up to fit the clock.
    \item Don't mention the phrasing constraint for updates (declarative ``X left Y'' works; ``can you update X'' is misclassified). That's an engineering limitation you fix, not a talking point.
\end{itemize}

\section{The five-beat demo, expanded (for a 2-minute window)}

If you have two minutes instead of thirty seconds, the pitch opens exactly the same way but the demo beat expands into a live walkthrough of all five demo messages:

\begin{enumerate}
    \item \textbf{Contact search} --- ``Hey, need someone in private equity in Joburg --- senior level, MD or Partner.'' Pipeline lights up; Alex gets a draft with 2--3 names; taps Send.
    \item \textbf{Follow-up pick} --- ``Connect me with the first one'' or ``Send me their details.'' Alex approves contact details (phone/email) before they go out.
    \item \textbf{Voice note} (optional) --- Record a 5-second voice note instead of typing. Same pipeline, Groq transcribes, same result --- shows multi-modal input.
    \item \textbf{Network update} --- ``Kara Davis left Andreessen Horowitz, she's at Bain Capital now.'' Alex sees \textbf{Update / Ignore} buttons; taps Update. DB changes live.
    \item \textbf{Named lookup} --- ``Do you know Kara Davis? Can I get her details?'' System returns the \emph{updated} company (Bain Capital, not Andreessen) --- proving the update landed.
\end{enumerate}

Beats 4 and 5 together are the moment that lifts this above ``smart search'': the network is a \emph{living} thing that gets more accurate every time Alex's friends share news, with Alex always in the loop.

\end{document}
